Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-22 writeup/gz_hubble_data.tex
GOODS comparisons to Bundy et al. (2005)

\subsection{Comparison to other catalogs}

@@

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item \sout{GEMS morphologies} \citep{hau07}
    \item \sout{AEGIS morphologies} \citep{lot08}
    \item GOODS N/S morphologies \citep{bun05}
\end{itemize}

@@

@@

\paragraph*{ACKNOWLEDGEMENTS.}

>>>>

\subsection{Comparison to other catalogs}\ref{ssec:comparisons}

@@

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item \sout{GEMS morphologies} \citep{hau07}
    \item \sout{AEGIS morphologies} \citep{lot08}
    \item \sout{GOODS N/S morphologies} \citep{bun05}
\end{itemize}

@@

\subsubsection{GOODS}

Galaxies in the GOODS-N and GOODS-S fields down to a limit of $z_{AB}=22.5$ have been visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band and composite $Viz$ color images \citep{bun05}. These morphologies are assigned a numerical value based on categories in \citet{bri98a}; these are combined into broader categories of ``E/S0'' (classes 0,1,2), ``Spirals'' (classes 3,4,5), and ``Peculiar/Irregular'' (classes 6,7,8). \citet{bun05} use these morphologies to show that there are an increasing proportion of early-type galaxies observed at later times.

Matching the \citet{bun05} catalog to GZH with a 0.5\arcsec{} radius yields 2435 galaxies (1300 in GOODS-N, 1135 in GOODS-S). We compare their broad morphological categories to \pbest{} in GZH; demographics of the separate GOODS-N and GOODS-S samples are highly consistent. ``E/S0'' galaxies are dominated by high smooth fractions in GZH, with an average value of $\langle p_\mathrm{smooth,best}\rangle=0.54\pm0.20$. The effect is stronger when examining sub-divisions; pure E galaxies have the highest $p_\mathrm{smooth,best}$ values, while S0 have the lowest. Visual inspection of galaxies designated as S0 show numerous examples of both edge-on galaxies and visible substructure in the disk, including spiral arms. This is consistent with the design of the GZH decision tree, and likely reflects that the expert categories are using different criteria.

``Spiral'' galaxies in \citet{bun05} have robustly high GZH vote fractions of features and/or disks, with $\langle p_\mathrm{features,best}\rangle=0.59\pm0.06$. The vote fraction increases with Hubble type, with Scd galaxies having the highest average \pbest{} values. ``Peculiar/Irregular'' galaxies have similar ranges of \pbest{} to the ``Spiral'' galaxies, but can be sub-selected with cutoffs on $p_\mathrm{odd}$ and $p_\mathrm{irregular}$ or $p_\mathrm{merger}$. We note that mergers are not strongly correlated in GZH and the expert visual classifications; between 20\%--30\% have GZH merger fractions of zero, while even clear tidal tails can be as low as $p_\mathrm{merger}\sim0.1$. The total number of major mergers is small enough that expert visual inspection can be practically done on all candidates; a combination of methods may be the most accurate way of identifying these rarer objects, especially when the signs of interaction are relatively subtle.

@@

\acknowledgments
